\section{Algorithm}
\label{sec:algorithm}

\subsection{Reason}

Using rapid and micro approach to do knowledge management should enable features corresponds to each personas listed here:%

\begin{easylist}[itemize]
  & As a person, I don't need to manually shout a new knowledge, so others can rapidly know what's the latest info then I can continue to do my study or work.
  & As a new user, I need to quickly use and understand the workflow, so I can immediately store my knowledge.
  & As a colleague of other user, I need to quickly know what other user have know, so I can learn from them.
  & As a student, I need to store and manage and find my knowledge easily, so I can neatly organize a preparation for study, exam, or portfolio.
  & As a teacher, I need to share my knowledge faster and effectively throughout the class or workshop, so I can focus on teaching and involving students to do the actual work precisely.
  & As a speaker, I need to liberate and outsource the presentation and discussion, so I with the audience can get the collaboration to live.
  & As a collaborator, I need to have the prerequisites to have, so I can work together at the same pace and level.
  & As the leader of some users in a team, I need to collect all their knowledge, so I can smarten and explain the knowledge.
  & As a recruiter of a new employee, I need to have the recruitees' knowledge in a consise and portable format, so I can compare and select who's the right candidate.
  & As a boss, I need to know what my employees are up to automatically, so I don't need to ask them rigorously.
  & As an engineer
  & As an information architect
  & As a developer, I need to be able to create a plugin or extension, so I can add more functionality to the system/platform.
  & As a designer, I need to be able to create a custom theme, so I can customize the appearance based on my style and taste.
  & As a researcher
\end{easylist}

