\section{Development}
\label{sec:development}

% --------------------------------------------------
\subsection{Language}

JavaScript is used on the client side and Node.js is used on the server side to properly implement the designed system.

% --------------------------------------------------
\subsection{Software Development Life Cycle}

\ldots

The development of system also follows or tends to assist a software development principle called \ac{DRY}\index{don't repeat yourself},
which every piece of knowledge must have a single, unambiguous, authoritative representation within a system.~\autocite{Hunt1999Pragmatic}
The code then resulted in a cleaner and clearer structure.
In detail, this applied in database schemas even we use a very flexible document database.
As well as test plans, the build system, and documentation within or outside the code.
Applied also in the user interaction design, therefore there is a decreased amount of duplicated data that is accidentally created or not intended by users.

% --------------------------------------------------
\subsection{Agile Process}

...

% --------------------------------------------------
\subsection{Minimum Viable \& Lovable Product (MVLP)}

...

% --------------------------------------------------
\subsection{Application Framework}

In early development, we need to use a \ac{WAF}\index{web application framework}, a software framework to make it easy to build web-enabled application from server-side to client-side applications.
Most popular \ac{WAF} now that also a full stack frameworks (not only a single stack frameworks) with full JavaScript technologies or heavily based on Node.js are: Meteor, DerbyJS, Sails.js, MEAN.IO, and MeanJS.
We choose full-stack frameworks because they're also have built in or bundled with various helpers such as librarires, template engines, protocol implementation, scaffolding, more integrated features, and even build system.
Today, most of them are real-time enabled up to easy to deploy and scale to meet modern standards of web application development.

% --------------------------------------------------
\subsection{Satellid Server}

...

% --------------------------------------------------
\subsection{Satellid Client}

...

