\section{Research Method}
\label{sec:research-method}

The research method we're using are essentially not traditionally adopted in most current academic environments.
Since the method is basically always following up with the latest and better way of thinking.
This attainment of doing is chosen because we need to constantly adjusting to the condition along the time, not just only determined in the first phase.
To make things leaner and more effective, we use agile methodologies to conduct the research, not only in development.
But in the interest of standard methodologies of research, there are several keys we can agree on.

\begin{description}
\item [Problem and Solution Discovery]: \hfill \\
Discovering problem and formulating solution for things around knowledge management which people are using and has problem with.
\item [Literature Study]: \hfill \\
Collecting and comprehending definition about knowledge management components, modern methodologies, database, chosen programming language, web application design, development, and framework, also open source involvement; inside books, online references, and research works.
\item [Analysis and Design]: \hfill \\
Applying the study into a resulted analysis and planned design.
\item [Implementation and Testing]. \hfill \\
Building the working implementation into a software then testing it.
\end{description}

In addition to these, agile methodologies imply that we should do iteration and improvement once it has been tested successfully.
Indeed, there will be some changes along the way that will affect parts of the defined methods.
