\section{Development}
\label{sec:development}

% --------------------------------------------------
\subsection{Agile Development}

%TODO As known before

Also, the \ac{SDLC} of this software follows or tends to assist a software development principle called \ac{DRY}\index{don't repeat yourself}, which every piece of knowledge must have a single, unambiguous, authoritative representation within a system,~\autocite{Hunt1999Pragmatic}
That means the content that potentially will be duplicated must only in a single part and be reusable.
Therefore code then resulted in a cleaner and clearer structure.
This applied as well as in test plans, the build system, and documentation within or outside the code.
Also happens in the user interaction design, therefore there is a decreased amount of duplicated data that is accidentally created or not intended by users.

In related to the primary logic that have been created, the following user stories are the list of features along with points that must be implemented sorted by priority.
The points are estimated by conjecture the required effort, in scale $1, 2, 3, 5, 8, 13$ (from easiest/shortest to hardest/longest).
The things which need to be prioritized in particular sequential order of implementation are: Read, Search, Add, Delete, Edit.

\begin{easylist}[enumerate]
& 1: As a System, I need to be run on supported platform and via a network
& 1: As a User, I want to use the app via web browser
& 2: As a System, I can have the data imported without the app opened
& 1: As a User, I want to read knowledge that already stored
& 3: As a User, I want to search a knowledge and view the search result
& 5: As a User, I want to add a new knowledge based on context
& 1: As a User, I want to delete a stored knowledge
& 3: As a User, I want to edit a stored knowledge
\end{easylist}

% --------------------------------------------------
\subsection{Code}

JavaScript and Meteor are used on both of the sides, while Node.js is used on the server side, all coded to implement the designed system.
JavaScript is chosen more solely because it is the primary language of the Web.
Meteor is chosen because it is heavily based on JavaScript and easy to learn than any other framework out there.

%TODO Some snippets...

% Server-Side

...

%TODO Input
%TODO Output

% Client-Side

...

%TODO Input
%TODO Output
