\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax

\chapter{Foreword}
\label{chap:foreword}

We as human definitely always think within our life everytime, gathering knowledge and creating wisdom based on information and data we have know. For some reason, there is no de facto way of gathering everyday knowledge in an effective system. Even we have live long enough to realize everything we had in mind should be organized or managed so we can use the most of our knowledge. Moreover, could be shared ubiquitously despite of the technology and people's boundary. This leads to what I've found a missing link in managing those in every occasion and place. It inspires me to create the new way of managing knowledge, better.

Sure we already have a lot of available tools around, especially note taking apps even general databases. But those tools are meant to be used for specific purposes. Such as company knowledge base, collaborated documents, todo or task lists, and others. But most of them don't have a system that can integrate with both digital and real world, mainly because we need to use the digital application to make the system work.

As a solution, I propose a new knowledge manager that doesn't like any other, that is very open by design at first. In the future, it is also rapid in experience, micro in size, modular in architecture components, structured in documents, linked for each knowledge, and can be transcluded with others. Along with this writing we will walk towards the ultimate knowledge manager that we can use everyday. Also explain why the current apps of managing knowledge could not fulfill the missing link through answering it in the form of a system. Hopefully this scientific writing and application could benefit in the advance of humanity up to the future.

This is my and our vision, to create a better way in managing our knowledge.

\endgroup
