\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax

\chapter{Preface}
\label{chap:preface}

First and foremost, praise and thanks raised to the Almighty, Allah SWT, for all blessing and also thanks utterance and good wishes sent to the prophet of Muhammad PBUH so, with all the grants, this work can be finished.

This work was made to complete the requirement to finish study in Undergraduate Program of Informatics Engineering Department, Gunadarma University. The title of this final project is "\myTitle".

Author also submit utterance thank you to every person who has not only assisted morale goodness but also gave a lot of material for this work. It is not possible to name everyone here; thanks go to all of them. However, author will dedicate special acknowledgment to:

\begin{easylist}
\ListProperties(Margin=0em)
& Prof. Dr. E. S. Margianti, SE., MM. as Rector of Gunadarma University.
& Prof. Suryadi Harmanto, S.Si., M.M.S.I. as second Rector Assistant of Gunadarma University.
%& Prof. Dr. Rernat. A. Benny Mutiara, SSi, SKom., as Dean of Computer.
& Prof. Dr. Ir. Bambang Suryawan, M.T. as Dean of Faculty of Industrial Technology.
& Dr.-Ing. Adang Suhendra, S.Si, S.Kom, M.Sc. as Head of Deparment of Informatics Engineering.
& Drs. Haryanto, M.M.S.I. as Director of SARMAG program.
& Dr. Edi Sukirman, S.Si., M.M. as Department Head of Bachelor's Defense Examination.
& Remi Sanjaya, ST., M.M.S.I. as Coordinator of SARMAG program.
& \mySupervisor, as author's supervisor of this work.
& All of SARMAG lecturers.
& Both parents who have always supported.
& Whole comrades at University Gunadarma.
& All parties who have helped this final settlement.
\end{easylist}

\pagebreak

As ordinary people, author apologize for any shortcomings and limitations in drafting this undergraduate thesis. Finally, author recognize that this study is far from perfect and still need more improvement, due to various limitations that the author had. So athor expect criticism and constructive suggestions for become improvement in the future. Hopefully this undergradudate thesis will be useful and can give some advantages for all of us. Amin.

\hfill

\begin{flushright}
  %\myCity, \myTime
  \myCity, \myDateSession
\end{flushright}

\hfill

\begin{flushright}
\myName
\end{flushright}

\endgroup
